\textbf{Modelling Neuroplasticity: Using Machine Learning to Learn About TMS Data}

### 2023-07-05 paper/paper.tex
.

The function $\rho$ represents the proportion between a potential $x$, evoked by
a paired stimulation, with respect to the average potential of single test
stimulations. On the other hand, $\delta$ is the average proportion of $x$
with respect to each single test pulse.

@@

\begin{theorem}
    Let $\pi$ denote the coefficient traditionally used for estimating the
    relative amplitude between test and paired pulses. In accordance to what was
    described in the second paragraph of Section $4$,

    \begin{align*}
        \pi = \frac{\mu_x}{\mu_t}
    .\end{align*}

    where $\mu_x, \mu_t$ are the mean paired and test pulse responses,
    respectively. It follows from the definition of $\pi$ and $\rho$ that

    \begin{align*}
        \pi = \frac{\rho(x_1, \textbf{t}) + \ldots + \rho(x_n, \textbf{t})}{n}
    .\end{align*}

@@

The second remark is of great importance. It states that the way in which
relative amplitude was traditionally computed---the way in which neuroplasticity
was traditionally proxied---is different from our proposed $\rho$ function only
in terms of scale. More specifically, the traditional coefficient used to proxy
neuroplasticity at the subject level is nothing but the mean $\rho$
measure in an experimental session. We believe this bestows $\rho$ with a
certain degree of confidence, insofar as not only it is not entirely new, but
neuroscientists have implicitly used it all along.

\begin{remark}
    Observe that 
    \begin{align*}
        \frac{\partial \rho}{\partial x } &= \frac{m}{\sum_{i = 1}^m
        t_j} \\ \frac{\partial \rho}{\partial t_i} &= -\frac{xm}{\big( \sum_{j =
        1}^m t_j \big)^2} \\ 
                    \frac{\partial \delta}{\partial x} &= \frac{1}{m}\sum_{i =
                    1}^m t_i \\ 
                        \frac{\partial \delta}{\partial t_i} &= -\frac{x}{mt_i^2}
    \end{align*}
\end{remark}

@@

\begin{definition}
    Let $\textbf{x} \in \mathbb{R}^j$ with $j \in \mathbb{N}$. Then $T:
    \mathbb{R}^j \to \mathbb{R}^j, R : \mathbb{R}^j \to \mathbb{R}^j$ are the
    linear transformations defined as

    $T(\textbf{x}) := \begin{bmatrix} 
        \rho(x_1) & \ldots & \rho(x_j)
    \end{bmatrix}^\intercal $ and $R(\textbf{x}) := \begin{bmatrix} 
        \delta(x_1) & \ldots & \delta(x_j) 
    \end{bmatrix}^\intercal $.
\end{definition}

@@

\begin{definition}
    Let $\mu^{(t)}_i$ be average test-pulse response of the $i$th subject. Let
    $\mu^{(t)^{-1}}_i$ be the average \textit{reciprocal} test-pulse response of
    the $i$th subject. Then $\textbf{M}^{k \times k}$ is a diagonal matrix with
    $\textbf{M}_{(ii)} := \frac{1}{\mu^{(t)}_{i}}$, and $\textbf{M'}^{~ k \times
    k}$ is a diagonal matrix with $\textbf{M'}_{ii} := \mu^{(t^{-1})}_i$.
\end{definition}

@@

We have expanded $\rho, \delta$ to higher dimensions for the purpose of
providing a theoretical framework of their application to larger data sets and
many experimental subjects. However, it is important to note that the matrix
representations here presented only make sense under the assumption that, on
each subject, none of $n$ paired pulses were anomalous, and hence all can be
safely included in the model. Such assumption rarely holds in reality, where it
is usual to excluded some pulses due to the presence of artifacts. There are
many ways to deal with this situation in the implementation of our model---the
safest being the direct application of $T$ and $R$ to the data vectors---. Thus,
more than serving the algorithmic implementation of the model, which may
prescind from them, these matrices provide insight into the exact nature of the
transformations involved in the model.

@@

@@

\begin{align*} 
    \frac{x}{m}\sum^m\frac{1}{t_j} &\geq \frac{xm}{\sum^m t_j} \\ 
    S_2^mS_1^m &\geq m^2
\end{align*}

@@

We know $S^k_1S^k_2 \geq k^2$ and then it suffices to show $t_{k+1}S_1^k +
\frac{S^k_2}{t_{k+1}}\geq 2k$. To prove this, simply observe that

@@

\textbf{Proof 2.} In \textbf{Remark 2}, we observe that $\rho$ is implicitly
used in the traditional measures of relative amplitude. Recall that such methods
consist in taking the average paired-pulse response and dividing it by the
average test-pulse response. It is easily observed that

\begin{align*} \frac{\mu_x}{\mu_d} = \frac{\frac{1}{n}\sum_{j=1}^n
        x_{j}}{\frac{1}{m}\sum_{j = 1}^m t_j} 
        = \frac{\rho(x_{1i})+\cdots + \rho(x_{ni})}{n}
\end{align*}

\begin{proof}[Theorem 1]

@@

    The proof the $R$ is linear is practically identical.
\end{proof}

>>>>

The function $\rho$ represents the proportion between a potential $x \in
\textbf{x}$ with respect to the average
potential of single test stimulations. On the other hand, $\delta$ is the
average proportion of $x$ with respect to each single test pulse.

@@

\begin{theorem}

    Let

    \begin{align*}
        \tau = \frac{\bar{x}}{\bar{t}}
    \end{align*}

    where $\bar{x}, \bar{t}$ are the average paired and test pulse responses,
    respectively. Then

    \begin{align*}
        \tau = \frac{1}{n} \sum_{i = 1}^n \rho(x_i, \textbf{t})
    \end{align*}

@@

Here, $\tau$ is the coefficient traditionally used for estimating the relative
amplitude between test and paired pulses (Lefaucher, 2019), in accordance to
what was described in the second paragraph of \textbf{Section 4}.

The previous theorem is of great importance. It states that the way in which
relative amplitude was traditionally computed---the way in which neuroplasticity
was traditionally proxied---is different from our proposed $\rho$ function only
in terms of scale. More specifically, the traditional coefficient used to proxy
neuroplasticity at the subject level is nothing but the mean $\rho$ measure in
an experimental session. We believe this bestows $\rho$ with a certain degree of
confidence, insofar as not only it is not entirely new, but neuroscientists have
implicitly used it all along.

@@

\begin{definition}
    Let $\textbf{x} \in \mathbb{R}^n$ with $n \in \mathbb{N}$. Then $T:
    \mathbb{R}^n \to \mathbb{R}^n, R : \mathbb{R}^n \to \mathbb{R}^n$ are the
    linear transformations defined as

    \begin{align*}
        T(\textbf{x}) &:= \begin{bmatrix} 
        \rho(x_1) & \ldots & \rho(x_n)
        \end{bmatrix}^\intercal \\ R(\textbf{x}) &:= \begin{bmatrix} 
        \delta(x_1) & \ldots & \delta(x_n) 
    \end{bmatrix}^\intercal
    \end{align*}

\end{definition}

@@

\begin{definition}
    Let $\overline{t}_i$ be average test-pulse response of the $i$th subject.
    Let $\hat{t}_i$ be the average of the \textit{reciprocal}
    responses on the $i$th subject. Then $\textbf{M}^{k \times k}$ is a diagonal
    matrix with $\textbf{M}_{(ii)} := \frac{1}{\overline{t}_i}$, and
    $\textbf{M'}^{~ k \times k}$ is a diagonal matrix with $\textbf{M'}_{ii} :=
    \hat{t}_i$.
\end{definition}

@@

We have expanded $\rho, \delta$ to higher dimensions for the purpose of
providing a theoretical framework of their application to larger data sets and
many experimental subjects. However, it is important to note that the matrix
representations here presented only make sense under the assumption that, on
each subject, none of $n$ paired pulses were anomalous, and hence all can be
safely included in the model. Such assumption rarely holds in reality, where it
is usual to excluded some pulses due to the presence of artifacts. There are
many ways to deal with this situation in the implementation of our model---the
safest being the direct application of $T$ and $R$ to the artifact-excluded data
vectors---. Thus, more than serving the algorithmic implementation of the model,
which may prescind from them, these matrices provide insight into the exact
nature of the transformations involved in the model.

@@

\subsection{Further theory}

Observe that

\begin{align*}
    \frac{\partial \rho}{\partial x } &= \frac{1}{\overline{t}}  \\ 
     \frac{\partial \rho}{\partial t_i} &= -\frac{x}{m\overline{t}^{~ 2}}
\end{align*}

We recall that $t_i, x_i \in \mathbb{R}^{+}$ by assumption, from which follows
that $\rho$ is constantly increasing with respect to $x$ and
decreasing with respect to $\textbf{t}$. Similarly,

\begin{align*} 
    \frac{\partial \delta}{\partial x} &= \overline{t}\\ 
    \frac{\partial \delta}{\partial t_i} &= -\frac{x}{mt_i^2}
\end{align*}

This result extends the property noted in \textbf{Theorem 1}. Namely, not only
is $\delta$ greater than $\rho$ for any $x$, but it also has a greater constant
rate of change when $t > 1$---which is always the case with non-anomalous EMG
peak to peak values.

Furthermore, we found that $\rho$ can be alternatively defined as

\begin{align*}
    \delta(x, \textbf{t}) = -\frac{x}{m}\int \frac{1}{t_i^2} dt_i \\ 
    \rho(x, \textbf{t}) &= -\frac{x}{m}\int \frac{1}{\overline{t}^2}
\end{align*}

\subsection{Proofs}

@@

\begin{align*} 
    &\frac{x}{m}\sum^m\frac{1}{t_j} \geq \frac{xm}{\sum^m t_j} \iff 
    S_2^mS_1^m \geq m^2
\end{align*}

@@

By hypothesis, $S^k_1S^k_2 \geq k^2$, and then it suffices to show $t_{k+1}S_1^k +
\frac{S^k_2}{t_{k+1}}\geq 2k$. To prove this, simply observe that

@@

\textbf{Proof 2.} In \textbf{Theorem 2}, we observed that $\rho$ is implicitly
used in the traditional measures of relative amplitude. Recall that such methods
consist in taking the average paired-pulse response and dividing it by the
average test-pulse response. It is easily observed that

\begin{align*} 
    \frac{\bar{x}}{\bar{t}}
         &= \frac{1}{n} \Big(\frac{ \sum_{i = 1}^n mx_i}{\sum_{i = 1}^m
             t_i}\Big) \\ 
         &= \frac{1}{n} \Big(\frac{ mx_1}{\sum_{i = 1}^m t_i} + \ldots + \frac{
             mx_n}{\sum_{i = 1}^m t_i}\Big) \\ 
         &= \frac{1}{n} \sum_{i = 1}^n \rho(x_i, \textbf{t})
\end{align*}

\begin{proof}[Theorem 3]

@@

    The proof that $R$ is linear is practically identical.
\end{proof}
